% ****** Start of file apssamp.tex ******
%
%   This file is part of the APS files in the REVTeX 4.2 distribution.
%   Version 4.2a of REVTeX, December 2014
%
%   Copyright (c) 2014 The American Physical Society.
%
%   See the REVTeX 4 README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.2
%
% See the REVTeX 4 README file
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex apssamp.tex
%  2)  bibtex apssamp
%  3)  latex apssamp.tex
%  4)  latex apssamp.tex
%
\documentclass[superscriptaddress,unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-2}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{physics}
\usepackage{lipsum}
\usepackage{subfig}
% \usepackage{braket}

%\newcommand\abs[1]{\left|#1\right|}
%\newcommand\bra[1]{\left| #1 \right \rangle}
%\newcommand\ket[1]{\left \langle #1 \right |}

\begin{document}


\title{Predicting Solid State Qubit Candidates}

\author{Oliver Lerstøl Hebnes}
\affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
\author{Marianne Etzelm\"uller Bathen}
\affiliation{Department of Physics and Center for Materials Science and Nanotechnology, University of Oslo, N-0316 Oslo, Norway}
\author{Øyvind Sigmundson Schøyen}
\affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
\author{Sebastian G. Winther-Larsen}
\affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
\author{Morten Hjorth-Jensen}
\affiliation{Facility for Rare Ion Beams and Department of Physics and Astronomy, Michigan State University, East Lansing, MI 48824, USA}
\affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
\author{Lasse Vines}
\affiliation{Department of Physics and Center for Materials Science and Nanotechnology, University of Oslo, N-0316 Oslo, Norway}

\begin{abstract}

Semiconductor materials provide a compelling platform for quantum
technology, and a vast amount of materials and their properties can be
found in high-throughput databases.  However, filtering among these
materials in order to find novel candidates for quantum technology is
a challenge. Therefore, we provide a framework for the automatic
discovery of promising solid-state material hosts using machine
learning methods.

We have developed data extraction tools for numerous material science
databases, and constructed over $4800$ physics-informed features for a
dataset consisting of more than $25000$ materials.  Furthermore, we
have developed and implemented three data mining approaches, termed
\textit{the Ferrenti approach}, \textit{the augmented Ferrenti
  approach} and \textit{the insightful approach} for defining three
distinct training sets for the supervised machine learning algorithms
logistic regression, decision tree, random forest and gradient boost
to be trained on.

We find a lack of consistent results for the Ferrenti approach and the
augmented Ferrenti approach due to an overly broad formulation of the
training set, whereas the restrictions set in the insightful approach
proved suitable. All models agreed on $214$ predicted candidates, with
examples such as ZnGeP$_2$, MgSe, CdS, BP, BC$_2$N, BP, Ge, GeC, InP,
and InAs. All approaches and all models agreed on a subset of $47$
eligible candidates of $8$ elemental, $29$ binary, and $10$ tertiary
compounds.

\end{abstract}

\pacs{02.70.Ss, 31.15.A-, 31.15.bw, 71.15.-m, 73.21.La}




\maketitle

\section{Introduction}


\section{Theoretical Background and Experimental Data} 

\section{Results and Discussions}

\section{Conclusions and Perspectives}


\begin{acknowledgments}

The work of MHJ is supported by the U.S. Department of Energy,
Office of Science, office of Nuclear Physics under grant
No. DE-SC0021152 and U.S. National Science Foundation Grants
No. PHY-1404159 and PHY-2013047.

\end{acknowledgments}

\bibliography{apssamp}% Produces the bibliography via BibTeX.
\end{document}

